%!TEX root = ../thesis.tex
\section{OVERVIEW}

% Write the description of this chapter

\subsection{GIS Tools for Accessibility Analysis}
\subsection{Modern Web-based Maps}
In our application the choice of maps library should be made. In this section several
libraries for maps drawing are reviewed. The pluses and minuses of each of the
library are considered.

\begin{description}

  % Google
  \item[Google Maps Javascript API] -- on of the most popular libraries
    on the list~\cite{google:maps}. \\
    \underline{\smash{Pluses:}}
    \begin{itemize}
      \item Maps styling.
      \item Supports different localization options.
      \item The most detailed map across the world.
      \item StreetView.
      \item Support for mobile devices.
    \end{itemize}

    \underline{\smash{Minuses:}}
    \begin{itemize}
      \item Does not support vector tiles.
      \item Limited support for custom tiles.
      \item Free until exceeding 25,000 map loads per 24 hours for 90 consecutive days.
    \end{itemize}

  % Leaflet
  \item[Leaflet.js] -- lightweight mobile-friendly interactive maps
    library~\cite{leaflet}. \\
    \underline{\smash{Pluses:}}
    \begin{itemize}
      \item Small size -- only 33 KB of JavaScript code.
      \item Relatively simple API.
      \item Support for custom tile sources.
      \item Support for multilayer maps.
      \item Considerable amount of plug-ins.
      \item Free and open-source.
    \end{itemize}

    \underline{\smash{Minuses:}}
    \begin{itemize}
      \item Does not support vector tiles.
      \item Lack of Russian localization.
    \end{itemize}

  % Yandex Maps
  \item[Yandex Maps] -- best maps fidelity in Russia~\cite{yandex:maps}. \\
    \underline{\smash{Pluses:}}
    \begin{itemize}
      \item Highly detailed maps of Russia.
      \item Support of Russian localization.
      \item No restrictions for map views.
    \end{itemize}

    \underline{\smash{Minuses:}}
    \begin{itemize}
      \item Does not support vector tiles.
      \item Does not support map styles.
      \item Does not support custom tiles rendering.
      \item Proprietary.
    \end{itemize}

  % Mapbox GL JS
  \item[Mapbox GL JS] -- only library with whole vector tiles support~\cite{gh:mapboxgljs}. \\
    \underline{\smash{Pluses:}}
    \begin{itemize}
      \item Supports vector tiles.
      \item Supports real-time maps styles.
      \item Supports custom tile source.
      \item Based on Leaflet API.
      \item Open source.
    \end{itemize}

    \underline{\smash{Minuses:}}
    \begin{itemize}
      \item Standard tile source has limitations on views per month.
      \item Not fully detailed map of Russia.
      \item Lack of Russian localization.
    \end{itemize}
\end{description}

\subsection{Data Formats}
\subsubsection{GeoJSON}
\subsubsection{MBTiles}
\subsubsection{Protocol Buffers}


